---
title: "Combustion Model"
author: "Anna Talucci"
date: '2022-09-28'
output: html_document
---

# Overview

Trouble shooting
https://stackoverflow.com/questions/30097730/error-when-using-predict-on-a-randomforest-object-trained-with-carets-train

# Library
```{r}
library(tidyverse)
library(ranger)
library(e1071)
library(arrow)
```
# Models
```{r}
above_model <- readRDS("../models/aboveground.rds")
below_model <- readRDS("../models/belowgrounds.rds")
depth_model <- readRDS("../models/burn_depth.rds")
```



# Landscape 1 Data
```{r}
landscape1_above = read.csv("../data/Landscape1/CombustionModel/Landscape1DataForCombustionModelABOVE.csv")
```

```{r}
landscape1_below = read.csv("../data/Landscape1/CombustionModel/Landscape1DataForCombustionModelBELOW.csv")
```

```{r}
l1_modeldata = read.csv("../data/Landscape1/CombustionModel/Landscape1DataForCombustionModel.csv")
```
```{r}
landscape1_above
landscape1_below
```


# Read in predictive data from stefano
```{r}
abovefed <- read_parquet("../data/TrainingDataFrame/abovefed_for_predict.parquet")
head(abovefed)
```

# Training Data
Original model training data.
```{r}
above_train =  read.csv("../data/TrainingDataFrame/aboveground.csv", header=TRUE, sep = ",", strip.white = TRUE)
```

```{r}
below_train =  read.csv("../data/TrainingDataFrame/belowground.csv", header=TRUE, sep = ",", strip.white = TRUE)
```

```{r}
above_importance =  read.csv("../data/TrainingDataFrame/aboveground_importance.csv", header=TRUE, sep = ",", strip.white = TRUE)
```

```{r}
below_importance =  read.csv("../data/TrainingDataFrame/belowground_importance.csv", header=TRUE, sep = ",", strip.white = TRUE)
```

# Check with AboveFed Training data
```{r}
setdiff(names(abovefed), names(l1_modeldata))
```

```{r}
setdiff(names(below_train), names(l1_modeldata))
```

```{r}
setdiff(names(above_train), names(l1_modeldata))
```

```{r}
setdiff(names(above_train), names(below_train))
```
```{r}
setdiff(below_importance$Variables, names(l1_modeldata))
```

```{r}
setdiff(above_importance$Variables, names(l1_modeldata))
```

```{r}
below_importance
```

#select only important variables
```{r}
above_train2 <- above_train %>% select(above_importance$Variables)
below_train2 <- below_train %>% select(below_importance$Variables)
above_train2$above.carbon.combusted = above_train$above.carbon.combusted
below_train2$below.ground.carbon.combusted = below_train$below.ground.carbon.combusted
```


# Training models 

Training each model with optimized parameters from Stefano's ABOVEFed Model
```{r}
model_ranger_above <- ranger(above.carbon.combusted ~., data = above_train2, mtry = above_model$bestTune$mtry, splitrule = above_model$bestTune$splitrule, min.node.size = above_model$bestTune$min.node.size)
```

```{r}
model_ranger_below <- ranger(below.ground.carbon.combusted ~., data = below_train2, mtry = below_model$bestTune$mtry, splitrule = below_model$bestTune$splitrule, min.node.size = below_model$bestTune$min.node.size)
```

```{r}
rownames(below_model$importance)
below_model$bestTune$splitrule
below_model$bestTune$mtry
below_model$bestTune$min.node.size
```



# Predict combustion with all independent variables
These predictive models use all independent variables.

```{r}
landscape1_above1 = landscape1_above %>% drop_na()
landscape1_below1 = landscape1_below %>%  drop_na()
```

```{r}
landscape1_above2 = landscape1_above1 %>% select(above_importance$Variables) 
landscape1_below2 = landscape1_below1 %>% select(below_importance$Variables) 
```

## Aboveground preditions 
```{r}
pred_above = predict(model_ranger_above, landscape1_above2)
```

```{r}
AbovepredResults <- data.frame(predict(model_ranger_above, landscape1_above2))
AbovepredResults
```

```{r}
above_pred <- cbind(landscape1_above1, AbovepredResults)
above_pred
```

```{r eval=FALSE, include=FALSE}
write_csv(above_pred, "../outputs/Landscape1PredictedAbovegroundCombustion.csv")
```

## Below Combustion
 
```{r}
pred_below = predict(model_ranger_below, landscape1_below2)
```

```{r}
BelowpredResults <- data.frame(predict(model_ranger_below, landscape1_below2))

```

```{r}
below_pred <- cbind(landscape1_below1, BelowpredResults)
```

```{r eval=FALSE, include=FALSE}
write_csv(below_pred, "../outputs/Landscape1PredictedBelowgroundCombustion.csv")
```

