---
title: "Combustion Model"
author: "Anna Talucci"
date: '2022-09-28'
output: html_document
---

# Overview

# Library
```{r}
library(tidyverse)
library(ranger)
library(e1071)
```
# Models
```{r}
model_above <- readRDS("../models/aboveground.rds")
model_below <- readRDS("../models/belowgrounds.rds")
model_depth <- readRDS("../models/burn_depth.rds")
```

```{r eval=FALSE, include=FALSE}
model_above 
```

# Training Data
```{r}
above_importance =  read.csv("../data/TrainingDataFrame/aboveground_importance.csv", header=TRUE, sep = ",", strip.white = TRUE)
below_importance =  read.csv("../data/TrainingDataFrame/belowground_importance.csv", header=TRUE, sep = ",", strip.white = TRUE)
```

#Training models 
Training each model with optimized parameters from Stefano ABOVEFed Model
```{r}
model_ranger_above <- ranger(y ~., data = df, mtry = final_model$bestTune$mtry, splitrule = final_model$bestTune$splitrule, min.node.size = final_model$bestTune$min.node.size)
```

```{r}
model_ranger_below <- ranger(y ~., data = df, mtry = final_model$bestTune$mtry, splitrule = final_model$bestTune$splitrule, min.node.size = final_model$bestTune$min.node.size)
```

# Predict
Not finished...
```{r}
predict(object=model_above, newdata = Landscape1, type="response", norm.votes=TRUE, predict.all=FALSE, proximity=FALSE, nodes=FALSE, cutoff, ...)
```


# Stefano's code (copied from Slack)

#read in the model I sent
```{r}
final_model <- readRDS(in_model)
```
#read in the dataframe initially used to train the model
```{r}
df = read_csv(training_frame)
```
#train new model using optimized paramaters
```{r}
  model_ranger_final <- ranger(y ~., data = df, mtry = final_model$bestTune$mtry, splitrule = final_model$bestTune$splitrule, min.node.size = final_model$bestTune$min.node.size)
```
#read in final data to predict on
```{r}
pred_df = read_csv(pred_frame)
```

#predict 
```{r}
 preds <- predict(model_ranger_final, data = pred_df)
```
#pul out predictions
```{r}
preds = preds$Preds
```
#read in the model I sent
```{r}
final_model <- readRDS(in_model)
```
#read in the dataframe initially used to train the model
```{r}
df = read_csv(training_frame)
```
#train new model using optimized paramaters
```{r}
model_ranger_final <- ranger(y ~., data = df, mtry = final_model$bestTune$mtry, splitrule = final_model$bestTune$splitrule, min.node.size = final_model$bestTune$min.node.size)
```
#read in final data to predict on
```{r}
pred_df = read_csv(pred_frame)
```
#predict 
```{r}
 preds <- predict(model_ranger_final, data = pred_df)
```
#pul out predictions
```{r}
preds = preds$Preds
```